---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: false
    smooth_scroll: true
---

```{r echo=FALSE, warning = FALSE, error = FALSE, message = FALSE}
library(rmarkdown)
library(tidyverse)
library(dplyr)
library(formattable)
library(tibble)
library(plotly)
library(DT)
doc_title <- snakemake@params[["title"]]
author_list <- snakemake@params[["authors"]]
author_list <- paste(author_list, collapse = ", ")
knitr::opts_chunk$set(warning = FALSE, # do not output warning messages
                      error = FALSE, # do not output error messages
                      echo = FALSE, # don't show code in report.
                      fig.width = 12, # set all figures to be 16 inches wide
                      fig.height = 6.75, # set all figures to be 9 inches tall
                      fig.align = 'center') # center align all figures
```

---
# title and author variables must be defined first.
title: "`r doc_title`"
author: "`r author_list`"
---

# Intro
`r snakemake@params[["intro"]]`

# Analysis
```{r results='asis'}
for (i in snakemake@params[["analysis"]]) {
	cat(paste("*", i, "\n"))
}
```

# Takeaways
```{r results='asis'}
for (i in snakemake@params[["takeaways"]]) {
	cat(paste("*", i, "\n"))
}
```

# Notes
`r snakemake@params[["notes"]]`

# Alignment {.tabset}

## General stats
```{r}
align_stats <- read.csv(snakemake@input[['align_stats']], header = F)
align_stats <- spread(align_stats, key=V2, value=V3)
align_stats <- align_stats %>%
    mutate(mito_rate = (starting_reads - no_ChrM) / starting_reads ) %>% 
    mutate(dup_rate = (starting_reads - no_duplicates) / starting_reads ) %>%
    mutate(hq_align = 1 - mito_rate - dup_rate)

align_stats <- align_stats %>% mutate_if(is.numeric, round, 2)
colnames(align_stats)[[1]] <- c("sample")
formattable::as.datatable(
  formattable(align_stats, list(
    mito_rate = color_bar("pink"),
    dup_rate = color_bar("pink")
)))
```
`mito_rate` = (starting_reads - reads w/out chrM) / starting_reads

`dup_rate` = (starting_reads - reads w/out duplicates) / starting_reads

`hq_align` = 1 - mito_rate - dup_rate

## FRiP
```{r}
frip_files <- list.files(snakemake@input[['frip_folder']], full.names = TRUE)
frip_df <- as.data.frame.list(lapply(frip_files, read.table, header = TRUE))
rownames(frip_df) <- c("outside", "inside")
frip_df <- as.data.frame(t(frip_df)) %>%
    rownames_to_column("sample") %>%
    mutate(ratio = inside / outside)
fig <- plot_ly(frip_df, x = ~ sample, y = ~ ratio, type = "bar", name = "inside_peaks", marker = list(color = 'rgb(255,201,57)'))
fig <- fig %>% add_trace(y = 1 - frip_df$ratio, name = "outside_peaks", marker = list(color = 'rgb(0,39,118)'))
fig <- fig %>% layout(title = "FRiP across all samples", yaxis= list(title = "fraction of reads", xaxis = list(title = "samples")), barmode = "stack")
fig
```

# Peaks {.tabset}

## Consensus peaks
The consensus peaks scheme is to find peaks that appear in 100% of replicates in at least one condition.
```{r}
consensus_stats <- read.table(snakemake@input[["consensus_stats"]], header = TRUE, check.names = FALSE)
consensus_stats <- consensus_stats %>% mutate_if(is.numeric, round, 2)
formattable::as.datatable(
  formattable(consensus_stats, list(
    `%_reads_in_CC` = color_bar("lightgreen")
)))
```

# Differential {.tabset}

## DE stats

```{r}
de_stats <- read.table(snakemake@input[["de_stats"]], header = TRUE)
formattable::as.datatable(
  formattable(de_stats, list(
    sig_peaks = color_bar("lightgreen")
)))
save.image()
```

## DE config

```{r}
contrasts <- read.table(snakemake@params[["contrasts"]], header = TRUE)
formattable::as.datatable(formattable(contrasts))
```
